---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Version: 0.4

### Features
* Updated plotting to create and return ggplot2 figures

* Backtest object creation now allows unquoted column names
```{r, eval=F}
backtest(x, in.var = "var.1", ret.var = "ret.var.1", by.period = FALSE)
# is identical to
backtest(x, in.var = var.1, ret.var = ret.var.1, by.period = FALSE)

# Also valid:
backtest(x, in.var = c(var.1, var.2), ret.var = ret.var.1, by.period = FALSE)
```

* Created functions to handle tidyverse verbs on backtest objects. Any operation on a backtest object creates a new backtest object.  Deprecated `universe` argument in backtest creation.

```{r, eval=F}
backtest(x, in.var = "var.1", ret.var = "ret.var.1", by.period = FALSE, universe = sector == "HiTec")
# should be  replaced with
backtest(x, in.var = var.1, ret.var = ret.var.1, by.period = FALSE)  %>% 
  filter(sector == "HiTec")

# Another example
backtest(x, in.var = var.1, ret.var = ret.var.1, by.period = FALSE)
    group_by(sector, date) %>%
    summarise(var.1 = max(var.1), ret.var.1 = mean(ret.var.1))

```

* New `backtest.update` function allows for quick updating of backtest object.  Function returns a new backtest object using the parameters of an existing backtest with any modifications in parameters as specified in the function call.
```{r, eval=F}
bt <- backtest(starmine, in.var = smi,
               ret.var = c(ret.0.1.m, ret.0.6.m), by.period = FALSE)
summary(bt)

bt2 <- backtest.update(bt, ret.var = ret.0.6.m)
summary(bt2)
## bt2 is identical to creating backtest(starmine, in.var = smi, 
##   ret.var = ret.0.6.m, by.period = FALSE)
```
### Internal Changes

* Package documentation ported to `roxygen2` framework.  Added documentation for all exposed functions.  Updated documentation to be in compliance with new CRAN standards.

* Created new (internal) functions `results` and `ret.stats` as accessor functions to backtest object parameters.

* Refactored backtest object creation to enable delayed execution for all calculation code. Calculation is deferred until the first time the data is accessed, such as when `summary` or `plot` is called. Deferred data includes objects formerly in the `object@results`, `object@turnover` and `object@ret.stats` slots. These slots have been removed, as the data now is accessed from the `object@calculated.data` environment. This change allows for the creation and updating of backtest objects through a series of `filter` or `mutate` operations without stopping to calculate results for intermediate objects.  Any validity checks and errors are still performed immediately.

* `summary(backtest)` now returns a list of its results to facilitate unit testing.

* Refactored `backtest.function` and `backtest.compute` into a single function.  Removed `backtest.compute.R`.

### Unit Testing
* Updated all unit tests to `"testthat"` framework

* Added unit tests for functions not previously tested (`.bt.spread`, `.bt.sharpe`)

* Added unit tests for backtest results using additional simulation parameters

* Added unit tests for all expected error and warning messages

* Added unit tests for tidyverse operations

* Added unit tests to verify that plotting completes

# Version: 0.3-1 (2013-07-08, released)

* Fixed spelling and grammar in comments.

# Version: 0.3-0 (2008-09-12, released)

* Added totalCounts method. Counts non-NA values that went into the calculation of spreads

* Method summaryStats made public.

* Fixed overlaps order of operations bug in backtest.function.

* Added returns and financials columns to starmine data.

# Version: 0.2-0 (2007-07-02, released)

* Added overlaps feature for controlling turnover.

* The user may specify a factor as in.var to define quantiles.

* Added by.period option for calculating quantiles within periods, now the default.

* Added do.spread option to toggle spread calculation.
	
# Version: 0.1-2 (2007-04-12, released)

* Fixed handling of the universe parameter.

* Added stop if there are quantiles with no observations.  Usually occurs with very little or very regular (usually synthesized) data.

* Updated 'backtest' vignette.
